% Created 2024-02-08 Thu 13:47
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\date{\today}
\title{Cover Letter}
\hypersetup{
 pdfauthor={},
 pdftitle={Cover Letter},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.1 (Org mode 9.7-pre)}, 
 pdflang={English}}
\begin{document}

\maketitle
\noindent
Dear Recruiting team,
\indent

I am writing to express my keen interest in the Lead IT Systems Analyst position at Aramco, as advertised. With a Ph.D. in Electrical Engineering and over eight years of research experience, particularly in AI and autonomous systems, I am excited about the opportunity to contribute to Aramco's innovative initiatives.

During my tenure as a Senior AI Consultant at NMK, an Autonomous Driving Company, I played a pivotal role in spearheading AI development projects aimed at enhancing the performance and capabilities of autonomous driving technologies. Collaborating closely with cross-functional teams, I led the optimization of AI algorithms, resulting in substantial improvements in the accuracy and reliability of NMK's assisted automated driving devices. Moreover, my role involved setting up experimental environments for testing the Autopilot on Carla Simulator, further honing my expertise in AI technologies.

One of my notable achievements at NMK was spearheading the development of an e-commerce platform, nmk.sa, which significantly increased sales volume by more than 50\%. This initiative underscored my ability to innovate and drive tangible business outcomes in dynamic environments.

My commitment to excellence extends beyond industry contributions. During my academic career, I published research papers in esteemed journals such as IEEE Access, showcasing my thought leadership and expertise in AI and autonomous driving domains. My doctoral work focused on developing advanced methods for Ensemble optimization in histological image classification, highlighting my ability to push the boundaries of technology and drive innovation.

I am particularly drawn to Aramco's commitment to technological advancement and sustainability. I am eager to leverage my diverse skill set and industry experience to drive digital transformation and operational excellence within the organization. With a passion for problem-solving and a track record of success, I am confident in my ability to lead high-performing teams and deliver solutions that propel Aramco forward in its mission.

Thank you for considering my application. I am excited about the opportunity to contribute to Aramco's continued success and would welcome the chance to discuss how my skills and experiences align with the organization's goals.

Warmest regards,

\noindent
Sincerely,\\[0pt]
Eid Alkhaldi, Ph.D.
\end{document}