% Created 2024-03-04 Mon 00:35
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\date{\today}
\title{Cover Letter}
\hypersetup{
 pdfauthor={},
 pdftitle={Cover Letter},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.1 (Org mode 9.7-pre)}, 
 pdflang={English}}
\begin{document}

\maketitle
\noindent
Dear Saudi Aramco Hiring Team,
\indent

I am writing to express my sincere interest in joining Saudi Aramco, an organization known for its commitment to excellence and innovation. With a Ph.D. in Electrical Engineering and over 8 years of experience in academic research and industry, I am excited about the opportunity to contribute to your team in a role that aligns with my expertise and interests.

Throughout my doctoral studies, I specialized in AI and autonomous systems, focusing on optimizing ensemble methods for Histological Image Classification. My research, published in respected journals such as IEEE Access, reflects my dedication to advancing knowledge and solving complex problems in technology and engineering.

In addition to my academic achievements, I have gained valuable industry experience as an AI Consultant at NMK and an Autonomous Driving Startup. In these roles, I led initiatives to develop AI-driven solutions, demonstrating my ability to innovate and deliver results in dynamic environments.

I am particularly drawn to Saudi Aramco's reputation for fostering innovation and collaboration to drive operational excellence. I am eager to contribute my expertise to support Saudi Aramco's mission and help the organization remain at the forefront of technological advancement.

I believe that my combination of academic rigor, industry experience, and passion for innovation positions me well to make meaningful contributions to Saudi Aramco. I am enthusiastic about the opportunity to bring my unique perspective to your team and contribute to the organization's continued success.

Thank you for considering my application. I am eager to discuss how my skills and experiences can benefit Saudi Aramco and contribute to achieving its goals. Please find my resume attached for your review.

Warmest regards,

\noindent
Sincerely,\\[0pt]
Eid Alkhaldi, Ph.D.
\end{document}