% Created 2023-10-14 Sat 22:23
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\date{\today}
\title{Cover Letter}
\hypersetup{
 pdfauthor={},
 pdftitle={Cover Letter},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.1 (Org mode 9.7-pre)}, 
 pdflang={English}}
\begin{document}

\maketitle
\noindent
Dear Center of Curriculum Development Recruiting team,
\indent


I hope this letter finds you well. I am Dr. Eid Alkhaldi, and I am writing to express my deep interest in joining the Center of Curriculum Development, an organization dedicated to enhancing educational materials and approaches. My passion and expertise in e-learning, artificial intelligence, and STEM education align seamlessly with your mission to improve curriculum development and educational quality.

My journey has been profoundly influenced by the transformative power of e-learning, with experiences on platforms like Coursera and DeepLearning.AI significantly impacting my academic and professional path. With a Ph.D. in Electrical Engineering and over eight years of experience in machine learning and artificial intelligence, I have built a strong foundation in computer science and statistics. This academic journey has cultivated my strong belief in the potential of technology to enhance learning, which aligns perfectly with your center's mission to improve curriculum development and educational efficiency.

I am confident that my dedication to advancing e-learning, coupled with my proficiency in AI, makes me a valuable addition to any team working towards similar objectives. I eagerly anticipate the opportunity to discuss how my skills and passion can contribute to your organization's mission and objectives.

Please find my attached resume for your reference. Thank you for considering my application.

Sincerely,

Eid Alkhaldi, Ph.D. 
\end{document}